% !TeX spellcheck = en_US
\RequirePackage{filecontents}
\begin{filecontents}{\jobname.bib}
	@article{art1,
		title = "Effective three-phase evolutionary algorithm to handle the large-scale colorful traveling salesman problem",
		journal = "Expert Systems with Applications",
		volume = "67",
		pages = "148 - 162",
		year = "2017",
		issn = "0957-4174",
		doi = "https://doi.org/10.1016/j.eswa.2016.09.022",
		url = "http://www.sciencedirect.com/science/article/pii/S0957417416305000",
		author = "Hassan Ismkhan",
		keywords = "The colorful TSP, Priority based crossover, Enhanced local search, Large-scale instances, H-3Ph-EA",
		abstract = "This paper proposes a novel evolutionary algorithm to handle the colorful traveling salesman problem. The proposed evolutionary algorithm is a three-phase algorithm and utilizes two types of a new crossover and an enhanced local search. In the first phase, quality of population is increased by applying the first crossover. After the first phase, a priority value is computed to each color, based on the best tour of the first phase. During the second phase, priority values are updated when a solution with better cost than existing solutions in population is found. Priority values are used by the second type of crossover, which is used in the second phase. After the second phase, the problem is converted to the classical traveling salesman problem ingeniously, and finally, the third phase is a hybrid genetic algorithm, for which an enhanced local search algorithm is applied. Applying the second type of crossover and updating priority values are continued in the third phase. The proposed algorithm is effective and finds new bounds for many large-scale instances and outperforms other state-of-the-art heuristic in terms of accuracy and speed. In many cases, gaps between results obtained by the proposed algorithm and the other methods are high. For some large-scale instances, proposed algorithm is 44 times faster than the other state-of-the-art competitor, which is the current most efficient algorithm."
	}
	
	@article{art2,
		issn = {2180-124X},
		abstract = {This paper presents a real-world case study of optimizing waste collection in Sweden. The problem, involving approximately 17,000 garbage bins served by three bin lorries, is approached as a travelling salesman problem and solved using simulation-based optimization and an evolutionary algorithm. To improve the performance of the evolutionary algorithm, it is enhanced with a repair function that adjusts its genome values so that shorter routes are found more quickly. The algorithm is tested using two crossover operators, i.e., the order crossover and heuristic crossover, combined with different mutation rates. The results indicate that the order crossover is superior to the heuristics crossover, but that the driving force of the search process is the mutation operator combined with the repair function.},
		journal = {International Journal Of Artificial Intelligence And Expert Systems},
		pages = {27--39},
		volume = {6},
		number = {3},
		year = {2015},
		title = {Simulation-based Optimization of a Real-world Travelling Salesman Problem Using an Evolutionary Algorithm with a Repair Function},
		author = {Syberfeldt, Anna and Rogstr\"om, Joel and Geertsen, Andr\'e},
		keywords = {Engineering And Technology ; Other Engineering And Technologies ; Other Engineering And Technologies Not Elsewhere Specified ; Teknik Och Teknologier ; Annan Teknik ; \"Ovrig Annan Teknik ; Evolutionary Algorithm ; Simulation-Based Optimization ; Travelling Salesman Problem ; Waste Collection ; Real-World Case Study ; Technology ; Teknik ; Production And Automation Engineering ; Produktion Och Automatiseringsteknik},
	}
	
	@inproceedings{art3,
		abstract = {The traveling salesman problem (TSP) is a famous NP-hard problem. The established evolutionary algorithms (EAs) cannot get satisfactory solutions of large or even medium scale TSP instances. To change this situation, a effective EA based on inver-over operator is introduced. In this algorithm, two novel crossover operators, the segment replacing crossover and the order adjusting crossover, are proposed. Moreover, a mechanism for changing the crossover and the mutation rate of the inver-over operator according to generations and a parameter, the critical value, is employed. The results of the experiment show that this new algorithm outperforms the basic EA based on the inver-over operator in all the 4 instances.},
		journal = {Mechatronic Science, Electric Engineering and Computer (MEC), 2011 International Conference on},
		pages = {2515--2517},
		publisher = {IEEE Publishing},
		isbn = {9781612847191},
		year = {2011},
		title = {A novel evolutionary algorithm for the traveling salesman problem},
		language = {eng},
		author = {Li, Chengjun and Xia, Yong and Xu, Si and Zhan, Wei},
	}
	@article{art4,
		issn = {0020-0255},
		abstract = {A novel adaptive hybrid crossover (AHX) is designed for MOEAs. The parameters setting in AHX is adjusted adaptively. AHX is embedded into five frameworks for solving MOPs. AHX is better than SBX and DE operators in solving most of test problems. In this paper, a novel recombination operator, called adaptive hybrid crossover operator (AHX), is designed for tackling continuous multiobjective optimization problems (MOPs), which works effectively to enhance the search capability of multiobjective evolutionary algorithms (MOEAs). Different from the existing hybrid operators that are commonly operated on chromosome level, the proposed operator is executed on gene level to combine the advantages of simulated binary crossover (SBX) with local search ability and differential evolution (DE) with strong global search capability. More opportunities are assigned to DE in the early evolutionary stage for gene-level global search in decision space; whereas, with the generation grows, more chances are gradually allocated to SBX for gene-level local search. The balance between the gene-level global and local search is well maintained by an adaptive control approach in AHX. To validate the effectiveness of AHX, it is studied by substituting the original recombination operators in the four state-of-the-art MOEAs (i.e., NSGA-II, SPEA2, SMS-EMOA, and MOEA/D), and the performance of revised algorithms is significantly improved. Furthermore, AHX is also compared to three recently proposed recombination operators, such as a newly DE inspired (DEI) recombination operator, a learning paradigm based on jumping genes (JGBL) and a bandit-based adaptive operator selection approach (FRRMAB). The experimental studies validate that AHX can be effectively integrated into different frameworks of MOEAs, and performs better than SBX, DE, DEI, JGBL and FRRMAB in solving various kinds of MOPs.},
		journal = {Information Sciences},
		pages = {177--198},
		volume = {345},
		publisher = {Elsevier Inc.},
		year = {2016},
		title = {A novel adaptive hybrid crossover operator for multiobjective evolutionary algorithm},
		language = {eng},
		author = {Zhu, Qingling and Lin, Qiuzhen and Du, Zhihua and Liang, Zhengping and Wang, Wenjun and Zhu, Zexuan and Chen, Jianyong and Huang, Peizhi and Ming, Zhong},
		keywords = {Evolutionary Algorithm ; Multiobjective Optimization ; Simulated Binary Crossover ; Differential Evolution},
	}
	
	@article{art5,
		issn = {1568-4946},
		abstract = {This paper proposes a many-objective evolutionary algorithm based on a projection-assisted intra-family election, called MOEA/PIE. This paper proposes the basic evolution direction, and a dominance relationship based evolution directions adaptive method. A novel projection-assisted intra-family election mechanism is integrated into the evolution procedure. The selection procedure based on angles adopts a dynamic deleting method. MOEA/PIE does not require a set of predefined reference points or weight vectors. In recent years, many researchers have put emphasis on the study of how to keep a good balance between convergence and diversity in many-objective optimization. This paper proposes a new many-objective evolutionary algorithm based on a projection-assisted intra-family election. In the proposed algorithm, basic evolution directions are adaptively generated according to the current population and potential evolution directions are excavated in each individual's family. Based on these evolution directions, a strategy of intra-family election is performed in every family and elite individuals are elected as representatives of the specific family to join the next stage, which can enhance the convergence of the algorithm. Moreover, a selection procedure based on angles is used to maintain the diversity. The performance of the proposed algorithm is verified and compared with several state-of-the-art many-objective evolutionary algorithms on a variety of well-known benchmark problems ranging from 5 to 20 objectives. Empirical results demonstrate that the proposed algorithm outperforms other peer algorithms in terms of both the diversity and the convergence of the final solutions set on most of the test instances. In particular, our proposed algorithm shows obvious superiority when handling the problems with larger number of objectives.},
		journal = {Applied Soft Computing Journal},
		pages = {394--411},
		volume = {61},
		publisher = {Elsevier B.V.},
		year = {2017},
		title = {A many-objective evolutionary algorithm based on a projection-assisted intra-family election},
		author = {Chen, Zefeng and Zhou, Yuren and Xiang, Yi},
		keywords = {Many-Objective Optimization ; Evolutionary Algorithm ; Evolution Direction ; Projection ; Angle},
	}
	
	@article{art6,
		issn = {0269-2821},
		abstract = {This paper is the result of a literature study carried out by the authors. It is a review of the different attempts made to solve the Travelling Salesman Problem with Genetic Algorithms. We present crossover and mutation operators, developed to tackle the Travelling Salesman Problem with Genetic Algorithms with different representations such as: binary representation, path representation, adjacency representation, ordinal representation and matrix representation. Likewise, we show the experimental results obtained with different standard examples using combination of crossover and mutation operators in relation with path representation.},
		journal = {Artificial Intelligence Review},
		pages = {129--170},
		volume = {13},
		publisher = {Kluwer Academic Publishers},
		number = {2},
		year = {1999},
		title = {Genetic Algorithms for the Travelling Salesman Problem: A Review of Representations and Operators},
		language = {eng},
		address = {Dordrecht},
		author = {Larra\~naga, P. and Kuijpers, C.M.H. and Murga, R.H. and Inza, I. and Dizdarevic, S.},
		keywords = {Travelling Salesman Problem ; Genetic Algorithms ; binary representation ; path representation ; adjacency representation ; ordinal representation ; matrix representation ; hybridation},
	}
	
	@article{art7,
		issn = {03029743},
		journal = {Lecture Notes in Computer Science (including subseries Lecture Notes in Artificial Intelligence and Lecture Notes in Bioinformatics)},
		pages = {803--812},
		volume = {1498},
		isbn = {3540650784},
		year = {1998},
		title = {Inver-over operator for the TSP},
		copyright = {Copyright 2013 Elsevier B.V., All rights reserved.},
		author = {Tao, G. and Michalewicz, Z.},
	}
	
	@article{art8,
		issn={2394-2320},
		title={Applying Map Reduction Technique with Genetic
			Algorithm Approach to Solve Travelling Salesman
			Problem}, 
		journal={International Journal of Engineering Research in Computer Science and Engineering},
		volume={4},
		issue={10},
		year={2017},
		keywords={Travelling Salesman Problem, Map Reduce, Genetic Algorithm.},
		url={https://www.technoarete.org/common_abstract/pdf/IJERCSE/v4/i10/Ext_01698.pdf}
	}
\end{filecontents}


\documentclass{article}

\usepackage{3201proj}
\usepackage[utf8]{inputenc}

\usepackage{biblatex}
\bibliography{\jobname}

\begin{document}
	{
		\parindent=0pt
		\bfseries
		Memorial University of Newfoundland \hfill Fall Semester 2018 
		
		Computer Science 3201 \hfill Submitted November 9\textsuperscript{th}
		
		\vskip 2pc
		
		{
			\Large \hfill Course Project Proposal \hfill
		}
	}
	
	\paragraph{Design Goals:} The goal of this project is to develop a fully functional evolutionary algorithm (EA) that will be capable of solving the travelling salesman problem (TSP) over three different datasets that vary in complexity; each data set representing a different country/location. In addition, this evolutionary algorithm will implement a novel and advanced technique that has previously been thoroughly researched to help increase the efficiency of the program.
	
	\paragraph{Techniques:} The main components of this evolutionary algorithm such as the main program and fitness, population and selection modules will be implemented using conventional means that have been covered during the instruction of this course. This evolutionary algorithm will implement the inver-over crossover stochastic mechanism. This method will essentially create offspring by combining unary crossover operators with the population driven characteristics of recombination; based on the concept of simple inversion by picking two random loci from the first parent and inversing its components. This process is then repeated with the resulting offspring and second parent until a condition is reached.
	
	\paragraph{Runtime Optimization:} According to the inver-over research that inspires the method used in this project, the number of times an individual is inversed along with the segments to be inverted (as they are based on other randomly selected individuals), would need to be optimized in order to boost the efficiency of the algorithm. 
	
	\paragraph{Team Management:} Task allocation is as follows.
	\begin{itemize}
		\item Omar Mohamed (201501962): project management, project write-up, assist with conventional TSP implementation, assist with advanced technique implementation.
		\item Jacob House (201614260): technical management, assist with write ups and create graphs and tables, final code logic check and assertions, assist with advanced technique implementation.
		\item Hassan El-Khatib (201504396): code documentation, implement runtime optimization, assist with project write-ups, assist with advanced technique implementation.
		\item Nabil Miri (201547429): basic conventional TSP implementation, assist with runtime optimization, assist with project write-ups, assist with advanced technique implementation.
	\end{itemize}
	
	\nocite{*}
	\printbibliography
\end{document}
