%% BREAK LINES EVERY 80 CHARACTERS TO HELP GIT WITH MERGING
\raggedbottom
As discussed in Section~\ref{ssec:hardware}, hardware limitations of the
computers used for algorithm execution were something that needed
to be considered and worked with in this project. Therefore, to 
facilitate an accurate and comprehensive report, hardware specifications
for all terminals used are included in this section. 


\subsection{Hosts Used}
A number of hosts belonging to Memorial's LabNet network were used to
run the GA developed for this report. These hosts are listed below.

\begin{verbatim}
   devastator.cs.mun.ca
   en2048ece03.engr.mun.ca
   en2048ece04.engr.mun.ca
   en2048ece05.engr.mun.ca
   en2048ece07.engr.mun.ca
   en2048ece12.engr.mun.ca
   laserbeak.cs.mun.ca
   overkill.cs.mun.ca
   pounce.cs.mun.ca
   starscream.cs.mun.ca
\end{verbatim}
Several other nodes were tested and not used due to lesser hardware 
capabilities.
\begin{verbatim}
   excalibur.cs.mun.ca
   excelsior.cs.mun.ca
   intrepid.cs.mun.ca
   reliant.cs.mun.ca
   valiant.cs.mun.ca
\end{verbatim}

\subsection{Processor Speed}
Specifications of the processor(s) in all nodes used for testing are 
included in Table~\ref{tab:cpu} on page~\pageref{tab:cpu}. 
\begin{table*}[ht]
	\centering\small
	\def\arraystretch{1.1}
	\begin{tabular}{lccccccc} \hline 
		\multirow{2}{*}{\bf Hostname} & \multirow{2}{*}{\bf Sockets} & \multirow{2}{*}{\parbox{1.75cm}{\centering\bf Cores per\\Socket}} & \multirow{2}{*}{\parbox{2cm}{\centering\bf Threads per Core}} & \multirow{2}{*}{\parbox{1.75cm}{\centering\bf CPU max.\\MHz}} & \multicolumn{3}{c}{\bf Cache}  \\ \cline{6-8}
		& & & & & {\bf L1} & {\bf L2} & {\bf L3} \\ \hline 
		|devastator| & 1 & 4 & 1 & 3800 & 32K & 256K & 6144K \\
		|en2048ece03| & 1 & 4 & 1 & 3600 & 32K & 256K & 6144K \\
		|en2048ece04| & 1 & 4 & 1 & 3600 & 32K & 256K & 6144K \\
		|en2048ece05| & 1 & 4 & 2 & 4000 & 32K & 256K & 8192K \\
		|en2048ece07| & 1 & 4 & 2 & 4000 & 32K & 256K & 8192K \\
		|en2048ece12| & 1 & 4 & 2 & 4000 & 32K & 256K & 8192K \\
		|excalibur| & 2 & 4 & 2 & 2668 & 32K & 256K & 8192K \\
		|excelsior| & 2 & 4 & 2 & 2668 & 32K & 256K & 8192K \\
		|laserbeak| & 1 & 4 & 1 & 3800 & 32K & 256K & 6144K \\
		|intrepid| & 2 & 4 & 2 & 2668 & 32K & 256K & 8192K \\
		|overkill| & 1 & 4 & 1 & 3800 & 32K & 256K & 6144K \\
		|pounce| & 1 & 4 & 1 & 3800 & 32K & 256K & 6144K \\
		|reliant| & 2 & 4 & 2 & 2668 & 32K & 256K & 8192K \\
		|starscream| & 1 & 4 & 1 & 3800 & 32K & 256K & 6144K \\ 
		|valiant| & 2 & 4 & 2 & 2668 & 32K & 256K & 8192K \\ \hline
	\end{tabular}
	\caption{Computer CPU Specifications\label{tab:cpu}}
\end{table*}

\subsection{Memory Specifications}
Due to conjecture made in Section~\ref{ssec:hardware} that one of the
limiting factors of the program execution time was random access 
memory (RAM) speed, an effort was made to retrieve these specifications
for the report. Unfortunately, due to system restrictions placed on 
LabNet computers, standard users do not have |sudo| privileges.
As a result, access to the |dmidecode| and |lshw| commands
needed to read information about system hardware is restricted.